Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-30 paper/paper.tex
add ref

\textit{Defunctionalization and Refunctionalization.}
\citeauthor{Reynolds:72} first shows defunctionalization as a program transformation 
technique that can be used to transform higher-order functions to first-order data types and 
its first-order dispatching function when writing definitional interpreters
\cite{Reynolds:72, Reynolds:HOSC98-revisited}. As generalized closure conversion,
defunctionalization is also used in program analysis, transformation, and partial evaluation. %TODO cite
Refunctionalization~\cite{Danvy:2006:RW:2171265.2171268, Danvy:2001:DW:773184.773202} is the 
left inverse of defunctionalization, firstly considered by \citeauthor{Danvy:2001:DW:773184.773202}.

>>>>

\textit{Defunctionalization and Refunctionalization.}
\citeauthor{Reynolds:72} first shows defunctionalization as a program transformation 
technique that can be used to transform higher-order functions to first-order data types and 
its first-order dispatching function when writing definitional interpreters
\cite{Reynolds:72, Reynolds:HOSC98-revisited}. As generalized closure conversion,
defunctionalization is widely used in compilation and analysis \cite{pottier2006polymorphic, 
Eisenberg:2014:PFT:2633357.2633361, fourtounis2014modular, 10.1007/3-540-46425-5_4, consel1993tour}.
Refunctionalization~\cite{Danvy:2006:RW:2171265.2171268, Danvy:2001:DW:773184.773202} as a 
left inverse of defunctionalization, was firstly considered by \citeauthor{Danvy:2001:DW:773184.773202}.
